Source Summaries

### 2020-04-19 paper/sourceSummaries/summary10.tex
prepped for the future summaries

\section{Summary 2}

@@

\noindent
Name of member

@@

\Urlmuskip=0mu plus 1mu\relax
\bibentry{filizzola2018security}

@@

\pagebreak

>>>>

\section{Summary 10}

@@

\noindent
Daniel Capps

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
%\bibentry{filizzola2018security}

@@

\noindent
\subsection{Trust and Security in RFID-Based Product Authentication System}

\noindent
Connor Leavesley

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{lehtonen07}

\noindent
The authors examine the trust and security of RFID authentication systems using a chain-of-trust model.

\noindent
The authors are using Classification Theory. A trust model is being constructed based on cases of misuse.

\noindent
The authors first agree on a definition of authentication. They use this definition to define a several types of authentication, such as location-based authentication. The authors construct the chains of trust and they look at threats and attacks. They then look at these chains for the risk of certain paths happening.

\noindent
RFID trust chains are highly complex and there are many threats faced in each chain. These chains are an effective method of mapping out trust and the threats faced to help authentication designers better secure their RFID environment.

\noindent
The authors offer no indication of a future direction of research.

\noindent
Joshua Niemann

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
%\bibentry{filizzola2018security}

\noindent
Jacob Ruud

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
%\bibentry{filizzola2018security}

\noindent
Quintin Walters

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
%\bibentry{filizzola2018security}

\Urlmuskip=0mu plus 1mu\relax
\pagebreak
